What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-15 android-stacks.tex
Pass over section III done.

\begin{figure*} 
\centering \includegraphics[width=\hsize]{studyoverview3.png}
\caption{Study overview.}\label{fig:overview} 
\end{figure*}

@@

\subsection{Manual Inspections}
\label{sec:manual}
In the context of the ExceptionMiner tool, manual inspections were used to:
(i) support on the identification of packages composing the Android platform, 
libs and apps analyzed in this study (as described previously); and (ii)  
identify the type of some exceptions reported on issues, 
that were not be automatically identified by the ExceptionMiner tool
(because they were defined on previous versions of libraries,
apps and Android Plaform). When the exception could not be  
found neither automatically, nor manually (because they were defined on a previous version
of the app or lib) the exception were classified 
in our study as ``Undefined".  Only 31 exceptions 
remained undefined - such exceptions were reported on 61 exception stack traces as 
presented in Table ~\ref{tab:typeroottab}.

\subsection{Replication Package}
All the data used in this study is publicly available at https://github.com/souzacoelho/exceptionminer.
Specifically we provide: (i) all issues related to Android projects found
in GITHub and Google Code used in this study; (iii) all stack traces extracted
from issues (ii) the results of manual inspection steps; (iv) the tool developed 
in this work to support stack trace extraction and distilling.

>>>>

\begin{figure*} 
\centering \includegraphics[width=.9\hsize]{studyoverview3.png}
\caption{Study overview.}\label{fig:overview} 
\end{figure*}

@@

\subsection{Manual Inspections}
\label{sec:manual}
In our experiments, the output of the ExceptionMiner tool was manually extended
in order to 
(i) support the identification of packages composing the Android platform, 
libs and apps analyzed in this study (as described previously); and (ii)  
identify the type of some exceptions reported in issues 
that were not be automatically identified by the ExceptionMiner tool
(because they were defined on previous versions of libraries,
apps and Android Plaform). When the exception could not be  
found automatically or manually (because they were defined on a previous version
of the app or lib), we classified the exception as ``Undefined''.  Only 31 exceptions 
remained undefined, which occurred in 60 different exception stack traces (see Table~\ref{tab:typeroottab}).

\subsection{Replication Package}
All the data used in this study is publicly available at \url{https://github.com/souzacoelho/exceptionminer}.
Specifically we provide: (i) all issues related to Android projects found
in GiTHub and Google Code used in this study; (ii) all stack traces extracted
from issues; (iii) the results of manual inspection steps; (iv) the
ExceptionMiner tool we developed to support stack trace extraction and distilling.
